Sensor Clusterization in D-optimal Design in Infinite Dimensional Bayesian Linear Inverse Problems

### 2024-08-22 revision/rev3.tex
Only need to comment on tekentrup

\AR I made sure the \href{https://github.com/yairdaon/OED}{repository}
is functioning and well-documented.

@@

\AR I appreciate the suggestion. I added a section reproducing the
abovementioned numerical experiments to the main article:

@@

\begin{figure}
    \centering
    \includegraphics[height=0.5\textwidth]{figs/simulations.png}
    \caption{Fraction of clustered $A$ for $AA^t = M$ and $M$
      generated randomly (see text and repository for details on
      generating $M$). It is evident that when $m-k \geq 2$ clusterization
      is ubiquitous, whereas for lower $m-k$ clusterization does not
      occur.}
  \label{fig:sim_AAt}
\end{figure}

@@

\begin{quote}

@@

\RC Experiment with the 1D heat equation: the experiment showcases
some interesting phenomena, but also raises many questions. For
instance: I would expect the dimensionality of the working domain
(here the unit interval [0, 1]) to play a role, since larger dimension
allow for higher freedom in placing the design points.

@@

\begin{quote}
  We choose a prior for the initial condition $u_0 \sim \mathcal{N}(0,
  (-\Delta)^{-1})$, with homogeneous Dirichlet boundary
  condition. This choice ensures the posterior is well-defined and
  prior realizations are well-behaved, see \cite[Theorem 3.1 and Lemma
    6.25]{Stuart10} for details.
\end{quote}

@@

\AR Basically I meant that its eigenvalues decrease "quickly". I
understand this is not a common or well-defined term so I removed the
relevant sentence.

@@

\AR I do not expect this conclusion to hold: if noise is
    present, even a repeated measurement will result in some
    information gain and an increase in design criterion, since the
    observation error is effectively reduced by a factor of
    $1/\sqrt{2}$ for the repeated measurement.

@@

\AR I explain this in more detail in the paper:

@@

\end{quote}
\begin{figure}\label{fig:eigenvectors}
  \centering
  \includegraphics[width=\textwidth]{figs/eigenvectors_dst_scaled.png}
  \caption{D-optimal measurement locations ($m=4$ measurements) and
    weighted eigenvectors for finding the initial condition of the 1D
    heat equation. Measurement locations and weighted eigenvectors are
    plotted over the computational domain $\Omega = [0, 1]$
    (x-axis). Measurement clusterization occurs approximately at
    $0.31$ and $0.69$. These two locations are a compromise between
    the magnitudes of the first and second eigenvectors, which are the
    eigenvectors that a D-optimal design aims to measure. Allocating
    $m=4$ measurements into two locations results in clusterization,
    according to the pigeonhole principle.}
  \label{fig:why}
\end{figure}

>>>>

\AR I made sure the repository is functioning and well-documented. See
\url{https://github.com/yairdaon/OED}.

@@

\AR I appreciate the suggestion. I added a section reproducing the
abovementioned numerical experiments to the main article. See Section
\ref{subsec:lemma_sims} reproduced below:

@@

\begin{figure}
    \centering
    \includegraphics[height=0.5\textwidth]{../latex/figs/simulations.png}
    \caption{Fraction of clustered $A$ for $AA^t = M$ and $M$
      generated randomly (see text and repository for details on
      generating $M$). It is evident that when $m-k \geq 2$ clusterization
      is ubiquitous, whereas for lower $m-k$ clusterization does not
      occur.}
  \label{fig:sim_AAt}
\end{figure}

@@

\begin{quote}
  DO THIS FML!!!!!!
\end{quote}

@@

\RC Experiment with the 1D heat equation: the experiment showcases
some interesting phenomena, but also raises many questions. For
instance: I would expect the dimensionality of the working domain
(here the unit interval $[0, 1]$) to play a role, since larger
dimension allow for higher freedom in placing the design points.

\AR Say something??? FML

@@

@@

\AR Basically I meant that its eigenvalues decay "quickly". I
understand this is not a common or well-defined term so I removed the
relevant sentence.

@@

\AR I do not expect this conclusion to hold: if noise is present, even
a repeated measurement will result in some information gain and an
increase in design criterion. The reason is that for that particular
measurement the signal-to-noise ratio increases: observation error is
effectively reduced by a factor of $1/\sqrt{2}$ for the repeated
measurement. I discuss this briefly in the revised manuscript:

\begin{quote}
  Clusterization should not be confused with replication. Replication
  requires that the experimentalist executes multiple trials under
  circumstances that are \emph{nominally identical} \cite[Section
    1.2.4]{morris2011}. Replication is commonly viewed as a beneficial
  and even necessary aspect of optimal experimental design
  \cite{fisher1949design, morris2011, schafer2001replication}. Similarly
  to a design implementing replication, a clustered design reduces the
  signal-to-noise ratio of the repeated measurements
  \cite{telford2007brief}. The difference is that a clustered design
  takes repeated measurements at the expense of other quantities not
  measured at all.
\end{quote}

@@

\AR I explain this in more detail in the revised manuscript:

@@

\begin{figure}\label{fig:eigenvectors}
  \centering
  \includegraphics[width=\textwidth]{figs/eigenvectors_dst_scaled.png}
  \caption{D-optimal measurement locations ($m=4$ measurements) and
    weighted eigenvectors for finding the initial condition of the 1D
    heat equation. Measurement locations and weighted eigenvectors are
    plotted over the computational domain $\Omega = [0, 1]$
    (x-axis). Measurement clusterization occurs approximately at
    $0.31$ and $0.69$. These two locations are a compromise between
    the magnitudes of the first and second eigenvectors, which are the
    eigenvectors that a D-optimal design aims to measure. Allocating
    $m=4$ measurements into two locations results in clusterization,
    according to the pigeonhole principle.}
  \label{fig:why}
\end{figure}
